Oregon Residential Lease Agreement
THIS AGREEMENT (hereinafter referred to as the "Oregon Lease Agreement")
is made and entered into this ____ day of _______________, 20____, by and between
___________________________________ (hereinafter referred to as "Landlord") and
________________________________________ (hereinafter referred to as "Tenant."
For and in consideration of the covenants and obligations contained herein and other
good and valuable consideration, the receipt and sufficiency of which is hereby
PROPERTY . Landlord
acknowledged, the parties hereto hereby agree as follows: 1.
owns certain real property and improvements located at ________________ (hereinafter referred to as
the "Property"). Landlord desires to lease the Premises to Tenant upon the terms and conditions
contained herein. Tenant desires to lease the Premises from Landlord on the terms and conditions as
contained herein.
2.
TERM.
This
Oregon
Lease
Agreement
shall
commence
on
________________________ andshall continue as a lease for term. The termination date shall
be on ___________________ at 11:59 PM. Upon termination date, Tenant shall be required to
vacate the Premises unless one of the following circumstances occur:
(i) Landlord and Tenant formally extend this Oregon Lease Agreement in writing or create
and execute a new, written, and signed Oregon Lease Agreement; or
(ii) Landlord willingly accepts new Rent from Tenant, which does not constitute past due
Rent.
In the event that Landlord accepts new rent from Tenant after the termination date, a month-to-
month tenancy shall be created. If at any time either party desires to terminate the month-to-
month tenancy, such party may do so by providing to the other party written notice of intention to
terminate at least 30 days prior to the desired date of termination of the month-to-monthtenancy.
Notices to terminate may be given on any calendar day, irrespective of Commencement Date. Rent shall
continue at the rate specified in this Oregon Lease Agreement, or as allowed by law. All other
terms and conditions as outlined in this Oregon Lease Agreement shall remain in full force and
effect. Time is of the essence for providing notice of termination (strict compliance with dates by
which notice must be provided is required). RENT. Tenant shall pay to Landlord the sum of
$______________ per month as Rent for the Term of the Agreement. Due date for Rent payment
shall be the 1st day of each calendar month and shall be considered advance payment for that
month. Weekends and holidays do not delay or excuse Tenant’s obligation to timely pay rent.
A.
Delinquent Rent. If not paid on the 1st, Rent shall be considered overdue and delinquent
on the 2nd day of each calendar month. If Tenant fails to timely pay any month’s rent,
Tenant will pay Landlord a late charge of $_________ per day until rent is paid in full. If
Landlord receives the monthly rent by the 3 rd day of the month, Landlord will waive the
late charges for that month. Any waiver of late charges under this paragraph will not
affect or diminish any other right or remedy Landlord may exercise for Tenant’s failure to
timely pay rent.4.
B. Prorated Rent. In the event that the Commencement Date is not the 1st of the calendar
month, Rent payment remitted on the Commencement Date shall be prorated based on a
30-day period.
C. Returned Checks. In the event that any payment by Tenant is returned for insufficient
funds ("NSF") or if Tenant stops payment, Tenant will pay $_________ to Landlord for
each such check, plus late charges, as described above, until Landlord
has received payment. Furthermore, Landlord may require in writing that Tenant pay all
future Rent payments by cash, money order, or cashier's check.
D. Order in which funds are applied. Landlord will apply all funds received from Tenant first to
any non-rent obligations of Tenant including late charges, returned check charges,
charge-backs for repairs, brokerage fees, and periodic utilities, then to rent, regardless of
any notations on a check.
E. Rent Increases. There will be no rent increases through the Termination Date. If this lease
is renewed automatically on a month to month basis, Landlord may increase the rent
during the renewal period by providing written notice to Tenant that becomes effective the
month following the 30 th day after the notice is provided.
SECURITY DEPOSIT. Upon execution of this Oregon Lease Agreement, Tenant shall deposit
with Landlord the sum of $_______________ (which amount is not in excess of two months
periodic rent) receipt of which is hereby acknowledged by Landlord, as security for any damage
caused to the Premises during the term hereof. Landlord may place the security deposit in an
interest bearing account and any interest earned will be paid to Landlord or Landlord’s
representative.
A. . REFUND. Upon termination of the tenancy, all funds held by the landlord as security
deposit may be applied to the payment of accrued rent and the amount of damages that the
landlord has suffered by reason of the tenant's noncompliance with the terms of this Oregon
Lease Agreement or with any and all laws, ordinances, rules and orders of any and all
governmental or quasi-governmental authorities affecting the cleanliness, use, occupancy and
preservation of the Premises.
B. DEDUCTIONS. Landlord may deduct reasonable charges from the security deposit for:
(1.) Unpaid or accelerated rent;
(2.) Late charges;
(3.) Unpaid utilities;
(4.) Costs of cleaning, deodorizing, and repairing the Property and its contents for
which Tenant is responsible;
(5.) Pet violation charges;
(6.) Replacing unreturned keys, garage door openers, or other security devices;
(7.) The removal of unauthorized locks or fixtures installed by Tenant;
(8.) Insufficient light bulbs;(9.) Packing, removing, and storing abandoned property;
(10.) Removing abandoned or illegally parked vehicles;
(11.) Costs of reletting, if Tenant is in default;
(12.) Attorney fees and costs of court incurred in any proceeding against Tenant;
(13.) Any fee due for early of removal of an authorized keybox;
(14.) Other items Tenant is responsible to pay under this Lease.
If deductions exceed the security deposit, Tenant will pay to Landlord the excess within ten days
after Landlord makes written demand. The security deposit will be applied first to any non-rent
items, including late charges, returned check charges, repairs, brokerage fees, and periodic
utilities, then to any unpaid rent.
5. USE OF PREMISES. The Premises shall be used and occupied solely by Tenant and Tenant's
immediate family, consisting of _____________________________________________,
exclusively, as a private single family dwelling, and no part of the Premises shall be used at any
time during the term of this Oregon Lease Agreement by Tenant for the purpose of carrying on
any business, profession, or trade of any kind, or for any purpose other than as a private single
family dwelling. Tenant shall not allow any other person, other than Tenant's immediate family or
transient relatives and friends who are guests of Tenant, to use or occupy the Premises without
first obtaining Landlord's written consent to such use. Tenant shall comply with any and all laws,
ordinances, rules and orders of any and all governmental or quasi-governmental authorities
affecting the cleanliness, use, occupancy and preservation of the Premises.
6. CONDITION OF PREMISES. Tenant stipulates, represents and warrants that Tenant has
examined the Premises, and that they are at the time of this Lease in good order, repair, and in a
safe, clean and tenantable condition.
7. ASSIGNMENT AND SUB-LETTING. Tenant shall not assign this Oregon Lease Agreement, or
sub-let or grant any license to use the Premises or any part thereof without the prior written
consent of Landlord. A consent by Landlord to one such assignment, sub-letting or license shall
not be deemed to be a consent to any subsequent assignment, sub-letting or license. An
assignment, sub-letting or license without the prior written consent of Landlord or an assignment
or sub-letting by operation of law shall be absolutely null and void and shall, at Landlord's option,
terminate this Oregon Lease Agreement.
8. ALTERATIONS AND IMPROVEMENTS. Tenant shall make no alterations to the buildings or
improvements on the Premises or construct any building or make any other improvements on the
Premises without the prior written consent of Landlord. Any and all alterations, changes, and/or
improvements built, constructed or placed on the Premises by Tenant shall, unless otherwise
provided by written agreement between Landlord and Tenant, be and become the property of
Landlord and remain on the Premises at the expiration or earlier termination of this Oregon Lease
Agreement.
9. NON-DELIVERY OF POSSESSION. In the event Landlord cannot deliver possession of the
Premises to Tenant upon the commencement of the Lease term, through no fault of Landlord or
its agents, then Landlord or its agents shall have no liability, but the rental herein provided shall
abate until possession is given. Landlord or its agents shall have thirty (30) days in which to give
possession, and if possession is tendered within such time, Tenant agrees to accept the demisedPremises and pay the rental herein provided from that date. In the event possession cannot be
delivered within such time, through no fault of Landlord or its agents, then this Oregon Lease
Agreement and all rights hereunder shall terminate.
10. HAZARDOUS MATERIALS. Tenant shall not keep on the Premises any item of a dangerous,
flammable or explosive character that might unreasonably increase the danger of fire or explosion
on the Premises or that might be considered hazardous or extra hazardous by any responsible
insurance company.
11. UTILITIES. Tenant shall be responsible for arranging for and paying for all utility services
required on the Premises.
12. MAINTENANCE, REPAIR, AND RULES. Tenant will, at its sole expense, keep and maintain the
Premises and appurtenances in good and sanitary condition and repair during the term of this
Oregon Lease Agreement and any renewal thereof. Without limiting the generality of the
foregoing, Tenant shall:
A. Not obstruct the driveways, sidewalks, courts, entry ways, stairs and/or halls, which shall be
used for the purposes of ingress and egress only;
B. Keep all windows, glass, window coverings, doors, locks and hardware in good, clean order
and repair;
C. Not obstruct or cover the windows or doors;
D. Not leave windows or doors in an open position during any inclement weather;
E. Not hang any laundry, clothing, sheets, etc., from any window, rail, porch or balcony nor air or
dry any of same within any yard area or space;
F. Not cause or permit any locks or hooks to be placed upon any door or window without the
prior written consent of Landlord;
G. Keep all air conditioning filters clean and free from dirt;
H. Keep all lavatories, sinks, toilets, and all other water and plumbing apparatus in good order
and repair and shall use same only for the purposes for which they were constructed. Tenant
shall not allow any sweepings, rubbish, sand, rags, ashes or other substances to be thrown
or deposited therein. Any damage to any such apparatus and the cost of clearing stopped
plumbing resulting from misuse shall be borne by Tenant;
I. Tenant's family and guests shall at all times maintain order in the Premises and at all places
on the Premises, and shall not make or permit any loud or improper noises, or otherwise
disturb other residents;
J. Keep all radios, television sets, stereos, phonographs, etc., turned down to a level of sound
that does not annoy or interfere with other residents;
K. Deposit all trash, garbage, rubbish or refuse in the locations provided and shall not allow any
trash, garbage, rubbish or refuse to be deposited or permitted to stand on the exterior of any
building or within the common elements;L. Abide by and be bound by any and all rules and regulations affecting the Premises or the
common area appurtenant thereto which may be adopted or promulgated by the
Condominium or Homeowners' Association having control over them.
13. DAMAGE TO PREMISES. In the event the Premises are destroyed or rendered wholly
uninhabitable by fire, storm, earthquake, or other casualty not caused by the negligence of
Tenant, this Oregon Lease Agreement shall terminate from such time except for the purpose of
enforcing rights that may have then accrued hereunder. The rental provided for herein shall then
be accounted for by and between Landlord and Tenant up to the time of such injury or destruction
of the Premises, Tenant paying rentals up to such date and Landlord refunding rentals collected
beyond such date. Should a portion of the Premises thereby be rendered uninhabitable, the
Landlord shall have the option of either repairing such injured or damaged portion or terminating
this Lease. In the event that Landlord exercises its right to repair such uninhabitable portion, the
rental shall abate in the proportion that the injured parts bears to the whole Premises, and such
part so injured shall be restored by Landlord as speedily as practicable, after which the full rent
shall recommence and the Oregon Lease Agreement continue according to its terms.
14. ACCESS BY LANDLORD. Landlord and Landlord's agents shall have the right at all reasonable
times, and by all reasonable means, without notice, during the term of this Oregon Lease
Agreement and any renewal thereof to enter the Premises for the following purposes:
A. Inspect the Property for condition;
B. Make repairs;
C. Show the Property to prospective tenants, prospective purchasers, inspectors, fire marshals,
lenders, appraisers, or insurance agents;
D. Exercise a contractual or statutory lien;
E. Leave written notice;
F. Seize nonexempt property after default.
Landlord may prominently display a “For Sale” or “For Lease” or similarly worded sign on the
Property during the term of this Lease or any renewal period.
If Tenant fails to permit reasonable access under this Paragraph, Tenant will be in default.
15. SUBORDINATION OF LEASE. This Oregon Lease Agreement and Tenant's interest hereunder
are and shall be subordinate, junior and inferior to any and all mortgages, liens or encumbrances
now or hereafter placed on the Premises by Landlord, all advances made under any such
mortgages, liens or encumbrances (including, but not limited to, future advances), the interest
payable on such mortgages, liens or encumbrances and any and all renewals, extensions or
modifications of such mortgages, liens or encumbrances.
16. TENANT'S HOLD OVER. If Tenant remains in possession of the Premises with the consent of
Landlord after the natural expiration of this Oregon Lease Agreement, a new tenancy from month-
to-month shall be created between Landlord and Tenant which shall be subject to all of the terms
and conditions hereof except that rent shall then be due and owing at $__________________ per
month and except that such tenancy shall be terminable upon fifteen (15) days written notice
served by either party.17. SURRENDER OF PREMISES. Upon the expiration of the term hereof, Tenant shall surrender the
Premises in as good a state and condition as they were at the commencement of this Oregon
Lease Agreement, reasonable use and wear and tear thereof and damages by the elements
excepted.
18. ANIMALS. THERE WILL BE NO ANIMALS, unless authorized by a separate written Pet
Addendum to this Residential Lease Agreement. Tenant shall not permit any animal, including
mammals, reptiles, birds, fish, rodents, or insects on the property, even temporarily, unless
otherwise agreed by a separate written Pet Agreement. If tenant violates the pet restrictions of
this Lease, Tenant will pay to Landlord a fee of $_____________ per day per animal for each day
Tenant violates the animal restrictions as additional rent for any unauthorized animal. Landlord
may remove or cause to be removed any unauthorized animal and deliver it to appropriate local
authorities by providing at least 24-hour written notice to Tenant of Landlord’s intention to remove
the unauthorized animal. Landlord will not be liable for any harm, injury, death, or sickness to any
unauthorized animal. Tenant is responsible and liable for any damage or required cleaning to the
Property caused by any unauthorized animal and for all costs Landlord may incur in removing or
causing any unauthorized animal to be removed.
19. WATERBEDS. THERE WILL BE NO WATERBEDS, unless authorized by a separate written
Waterbed Addendum to this Residential Lease Agreement.
20. QUIET ENJOYMENT. Tenant, upon payment of all of the sums referred to herein as being
payable by Tenant and Tenant's performance of all Tenant's agreements contained herein and
Tenant's observance of all rules and regulations, shall and may peacefully and quietly have, hold
and enjoy said Premises for the term hereof.
21. INDEMNIFICATION. Landlord shall not be liable for any damage or injury of or to the Tenant,
Tenant's family, guests, invitees, agents or employees or to any person entering the Premises or
the building of which the Premises are a part or to goods or equipment, or in the structure or
equipment of the structure of which the Premises are a part, and Tenant hereby agrees to
indemnify, defend and hold Landlord harmless from any and all claims or assertions of every kind
and nature.
22. DEFAULT. If Landlord breaches this Lease, Tenant may seek any relief provided by law. If
Tenant fails to comply with any of the material provisions of this Oregon Lease Agreement, other
than the covenant to pay rent, or of any present rules and regulations or any that may be
hereafter prescribed by Landlord, or materially fails to comply with any duties imposed on Tenant
by statute, within seven (7) days after delivery of written notice by Landlord specifying the non-
compliance and indicating the intention of Landlord to terminate the Lease by reason thereof,
Landlord may terminate this Oregon Lease Agreement. If Tenant fails to pay rent when due and
the default continues for seven (7) days thereafter, Landlord may, at Landlord's option, declare
the entire balance of rent payable hereunder to be immediately due and payable and may
exercise any and all rights and remedies available to Landlord at law or in equity or may
immediately terminate this Oregon Lease Agreement.
23. ABANDONMENT. If at any time during the term of this Oregon Lease Agreement Tenant
abandons the Premises or any part thereof, Landlord may, at Landlord's option, obtain
possession of the Premises in the manner provided by law, and without becoming liable to
Tenant for damages or for any payment of any kind whatever. Landlord may, at Landlord's
discretion, as agent for Tenant, relet the Premises, or any part thereof, for the whole or any part
thereof, for the whole or any part of the then unexpired term, and may receive and collect all rent
payable by virtue of such reletting, and, at Landlord's option, hold Tenant liable for any difference
between the rent that would have been payable under this Oregon Lease Agreement during the
balance of the unexpired term, if this Oregon Lease Agreement had continued in force, and the
net rent for such period realized by Landlord by means of such reletting. If Landlord's right ofreentry is exercised following abandonment of the Premises by Tenant, then Landlord shall
consider any personal property belonging to Tenant and left on the Premises to also have been
abandoned, in which case Landlord may dispose of all such personal property in any manner
Landlord shall deem proper and Landlord is hereby relieved of all liability for doing so.
24. ATTORNEYS' FEES. Should it become necessary for Landlord to employ an attorney to enforce
any of the conditions or covenants hereof, including the collection of rentals or gaining
possession of the Premises, Tenant agrees to pay all expenses so incurred, including a
reasonable attorneys' fee.
25. RECORDING OF OREGON LEASE AGREEMENT. Tenant shall not record this Oregon Lease
Agreement on the Public Records of any public office. In the event that Tenant shall record this
Oregon Lease Agreement, this Oregon Lease Agreement shall, at Landlord's option, terminate
immediately and Landlord shall be entitled to all rights and remedies that it has at law or in equity.
26. GOVERNING LAW. This Oregon Lease Agreement shall be governed, construed and interpreted
by, through and under the Laws of the State of Oregon.
27. SEVERABILITY. If any provision of this Oregon Lease Agreement or the application thereof
shall, for any reason and to any extent, be invalid or unenforceable, neither the remainder of this
Oregon Lease Agreement nor the application of the provision to other persons, entities or
circumstances shall be affected thereby, but instead shall be enforced to the maximum extent
permitted by law.
28. BINDING EFFECT. The covenants, obligations and conditions herein contained shall be binding
on and inure to the benefit of the heirs, legal representatives, and assigns of the parties hereto.
29. DESCRIPTIVE HEADINGS. The descriptive headings used herein are for convenience of
reference only and they are not intended to have any effect whatsoever in determining the rights
or obligations of the Landlord or Tenant.
30. CONSTRUCTION. The pronouns used herein shall include, where appropriate, either gender or
both, singular and plural.
31. NON-WAIVER. No delay, indulgence, waiver, non-enforcement, election or non-election by
Landlord under this Oregon Lease Agreement will be deemed to be a waiver of any other breach
by Tenant, nor shall it affect Tenant's duties, obligations, and liabilities hereunder.
32. MODIFICATION. The parties hereby agree that this document contains the entire agreement
between the parties and this Oregon Lease Agreement shall not be modified, changed, altered or
amended in any way except through a written amendment signed by all of the parties hereto.
33. NOTICE. Any notice required or permitted under this Lease or under state law shall be delivered
to Tenant at the Property address, and to Landlord at the following address:
_______________________________________________________________________
34.
LEAD-BASED PAINT DISCLOSURE.
If the premises were constructed prior to 1978, Tenant
acknowledges receipt of the form entitled “LEAD-BASED PAINT DISCLOSURE” which contains
disclosure of information on lead-based paint and/or lead-based paint hazards.
As to Landlord this ______ day of ________________________, 20_____.LANDLORD:
Sign: ___________________________________
Print: _________________________________ Date: ______________
As to Tenant, this ______ day of ________________________, 20_____.
TENANT
Sign: ___________________________________
Print: __________________________________ Date: ______________
TENANT:
Sign: ___________________________________
Print: __________________________________ Date: ______________
